Bullet Groups as a test of $\Lambda$CDM

### 2014-03-03 paper/ms.tex
article

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

@@

\begin{abstract}
We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that the probability of finding a system
similar with displacements of $\sim$400 kpch$^{-1}$ is between 40\%
for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
correspond to the observational constraint the object SL2S J08544-0121
that is  a gravitational lens found in the SL2S and located at
z$=0.35$. Given the larger abundance of groups with respect to
clusters, finding multi-modal groups and baryonic-dark matter
displacements.  
\end{abstract}

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=0.90\textwidth]{Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
\label{configuration}
\end{figure*}

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
\end{center}
\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$
  vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
  line correpond to
  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the
  red star simbol correspond to
  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S
  SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
  are the sample with circular velocities $>700$ kms$^{-1}$ and the
  four down panels are the sample with  circular velocities between
  300 km s$^{-1}$ to 700 kms$^{-1}$.} 
\label{newparameter}
\end{figure*}

\begin{figure*}
\begin{center}
%\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
  for the projection (X,Y). {\bf Left panel:} Sample with
  $\nu_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
  dashed line, correspond to the separation between dark matter to
  dark matter estimate in this work as the double of separation
  between the collisional gas and dark matter of 124$\pm$20 kpc
  reported by \citet{Gastaldello} for the group SL2S J08544-0121.
  {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
  kms$^{-1}$ for different redshifts.}  
\label{displacements}
\end{figure*}

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
where the substructure is emerging from the host halo and  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cos_theta}
\end{figure*}

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cumulative_cos}
\end{figure*}

>>>>

%\documentclass{emulateapj}
\documentclass{aastex}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

@@

\begin{abstract}

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that the probability of finding a system
similar with displacements of $\sim$400 kpch$^{-1}$ is between 40\%
for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
correspond to the observational constraint the object SL2S J08544-0121
that is  a gravitational lens found in the SL2S and located at
z$=0.35$. Given the larger abundance of groups with respect to
clusters, finding multi-modal groups and baryonic-dark matter
displacements.  
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.90\textwidth]{Figures_eps/Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
\label{configuration}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
\end{center}
\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$
  vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
  line correpond to
  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the
  red star simbol correspond to
  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S
  SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
  are the sample with circular velocities $>700$ kms$^{-1}$ and the
  four down panels are the sample with  circular velocities between
  300 km s$^{-1}$ to 700 kms$^{-1}$.} 
\label{newparameter}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
  for the projection (X,Y). {\bf Left panel:} Sample with
  $\nu_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
  dashed line, correspond to the separation between dark matter to
  dark matter estimate in this work as the double of separation
  between the collisional gas and dark matter of 124$\pm$20 kpc
  reported by \citet{Gastaldello} for the group SL2S J08544-0121.
  {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
  kms$^{-1}$ for different redshifts.}  
\label{displacements}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
where the substructure is emerging from the host halo and  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cos_theta}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cumulative_cos}
\end{figure*}
